% !TeX spellcheck = en_US
\documentclass[
    10pt,
    A4,
    english,
    draft = false,
    twoside = false,
]{article}

\usepackage{curriculum-vitae}

\begin{document}
	%	Basic information	
	\setname{Amrit}{Rathie}
	\setaddress{Grapevine, Texas}
	\setmobile{(817) 888 1378}
	\setmail{amrit.rathie@utdallas.edu}
	\setlinkedin{https://www.linkedin.com/in/amrit-rathie-9952a7224/}
	\setgithub{https://github.com/Spaceface16518}
	\setblog{https://www.amritr.xyz/posts}
	
	%---------------------------------------------------------------------------------------
	%	Title + Contact
	%----------------------------------------------------------------------------------------
	\cvtitle{Resume}
	%---------------------------------------------------------------------------------------
	%	Summary / Objectives
	%----------------------------------------------------------------------------------------
	\cvSection{Summary}
	\CVTextBlock{Computer Science student interested in Systems Programming and Administration, Infrastructure management, and Cybersecurity. I have contributed to many open-source projects using a variety of languages and tools, and am looking to increase my exposure to real-world, corporate use-cases. I'm a versatile programmer and a quick learner, committed to using the right tool for each task.}
	%---------------------------------------------------------------------------------------
	%	Current Position
	%----------------------------------------------------------------------------------------
%	\cvSection{Current Position}
	%---------------------------------------------------------------------------------------
	%	Education
	%----------------------------------------------------------------------------------------
	\cvSection{Education}
	\CVBlockWithTime{The University of Texas at Dallas}{2021 - Present}
	{BS in Computer Science, expected graduation: May 2025}{Richardson, Texas}
	{\textbf{GPA:} 3.22}
	\CVBlockWithTime{Grapevine High School}{2018 - 2021}
	{Multi-disciplinary studies}{Grapevine, Texas}
	{\textbf{GPA:} 4.2}
	%---------------------------------------------------------------------------------------
	%	Experience (Research and Industry)
	%----------------------------------------------------------------------------------------
%	\cvSection{Experience (Research \& Industry)}
	\cvSection{Experience}
	\CVBlockWithTime{Mobile Applications Development Intern}{Summer 2020}{ObjectWin, Inc.}{Houston, Texas (Remote)}
	{Worked with an \textbf{international team} to develop an internal timesheet entry \textbf{mobile application} for tech consulting company ObjectWin. Learned to work with a team across time \& language barriers, using tools of a modern workplace. \textbf{Reduced operational overhead} for consultants by optimizing non-billable time. \\ \textbf{AngularJS \cvContactSpace Ionic \cvContactSpace SQL Server}}
	\CVBlockWithTime{ACM Research}{Fall 2021}{ACM UTD}{Richardson, Texas}
	{Worked with a talented team to perform detailed analysis of \textbf{Swarm Robotics Algorithms}. Utilized \textbf{modern simulation technology} to model \textbf{real-world use of cutting-edge algorithms}, and used \textbf{popular data analysis tools} to explore results of simulation. Reduced data analysis run-time by \textbf{99.89\%} using advanced parallelism and caching techniques. \\ \textbf{C++ (Unreal Engine) \cvContactSpace Python (Pandas, Seaborn, Joblib)}}
	% TODO: soft skills
	%---------------------------------------------------------------------------------------
	%	Skills
	%----------------------------------------------------------------------------------------
	\cvSection{Skills}
	\tab \begin{tabular}{r p{0.7\textwidth}}
		\texttt{\large Programming Languages} & \textbf{Expert:} Rust \cvContactSep Python \\ & \textbf{Experienced:} Go \cvContactSep JavaScript \cvContactSep SQL \\ & \textbf{Familiar:} C \cvContactSep C++ \cvContactSep Java \cvContactSep Haskell \cvContactSep Bash \cvContactSep \LaTeX \cvContactSep X86, MIPS, \& ARM Assembly\\
		\texttt{\large Tools} & Git \cvContactSep Linux \cvContactSep Docker \cvContactSep Ansible \cvContactSep Kubernates \cvContactSep Cloudflare \cvContactSep AWS \cvContactSep Postgres \\
		\texttt{\large Libraries} & Numpy \cvContactSep Pandas \cvContactSep Seaborn \cvContactSpace Vue.js \cvContactSep React \cvContactSpace Gin \cvContactSpace Tokio \cvContactSep Clap \cvContactSep Eyre \cvContactSep Criterion \cvContactSep Serde \cvContactSep Nom\\
		\texttt{\large Languages} & \textbf{Native:} English \\ & \textbf{Beginner:} Hindi \cvContactSep Marathi \cvContactSep American Sign Language \\
	\end{tabular}\\~\\
	
	\newpage
	
	%---------------------------------------------------------------------------------------
	%	Awards and Distinction
	%----------------------------------------------------------------------------------------
	\cvSection{Honors \& Awards}
	\CVBlockWithTime{National AP Scholar}{2020}{Grapevine High School}{United States}
	{Granted to students in the United States who receive an average score of at least 4 on all AP Exams taken, and scores of 4 or higher on eight or more of these exams.}
	\CVBlockWithTime{AP Scholar with Distinction}{2019 \cvContactSep 2020 \cvContactSep 2021}{Grapevine High School}{Global}
	{Granted to students who receive an average score of at least 3.5 on all AP Exams taken, and scores of 3 or higher on five or more of these exams.}
	\CVBlockWithTime{Director's Choice}{2021}{Grapevine High School Band}{Grapevine, Texas}
	{Offered to two students per year that exemplify core values of the Grapevine High School Band.}
	%---------------------------------------------------------------------------------------
	%	Teaching Experience
	%----------------------------------------------------------------------------------------
%	\cvSection{Teaching Experience}	
	%---------------------------------------------------------------------------------------
	%	Extra Curricular Activities
	%----------------------------------------------------------------------------------------
%	\newpage
	\cvSection{Extracurricular Activities}
	\CVBlockWithTime{Band Leadership Team}{2019 - 2020}{Grapevine High School Band}{Grapevine High School}
	{Served as flute section leader of the Grapevine High School band, managing training of new members, uniform logistics, social events, and coordination with other leaders.}
	%---------------------------------------------------------------------------------------
% 	\cvSection{Teaching Experience}
% 	\cvSection{Professional Activities}
% 	\cvSection{Invited Talks}
% 	\cvSection{Selected Press Coverage}
% 	\cvSection{Publications}
	%----------------------------------------------------------------------------------------
\end{document}
