\cvsection{Projects}

\begin{cventries}

\cventry
{HackUTD \color{lightgray} (Largest University Hackathon in Texas)}
{Septre Insights \color{gray} (Diagnose 7 diseases with a smartphone)}
{HackUTD VIII}
{Nov 2021}
{
\begin{cvitems}
\item {Augmented retinal fundoscopy dataset to train PyTorch Machine Learning
	Model.}
\item {Used ML model to diagnose 7 different diseases, including diabetes and
	glaucoma, using digital fundoscopy with over 85\% accuracy.}
\item {Developed Vue.js Frontend and Swift Mobile App connected to Flask API with PostgreSQL Backend.}
\end{cvitems}
}

\cventry
{UTD Nebula \color{lightgray} (Student Organization creating Open Source Software for Students)}
{Degree Planner \color{gray} (Drag and drop degree planner app for UTD courses)}
{The University of Texas at Dallas}
{Fall 2022}
{
\begin{cvitems}
\item {Implemented Course Validation functionality, allowing users to
	automatically verify the validity of their class schedule.}
\item {Contributed Degree Plan Validation functionality, enabling automatic auditing of a degree plan without an advisor.}
\item {Mentored a group of 4 students on frontend technologies HTML/CSS/JS,
	TypeScript, and Next.js.}
\end{cvitems}
}

\cventry
{ACM Research \color{lightgray}(12-week research competition)}
{Comparison of Swarm Robotics Algorithms \color{gray} (Cooperation of a swarm
	of simple robots)}
{The University of Texas at Dallas}
{Fall 2021}
{
\begin{cvitems}
\item {Compared 3 algorithms for controlling robotics with decentralized control
	and cooperation.}
\item {Designed realistic simulation using C++ and Unreal Engine to collect
	behavioral data of robots performing resource collection tasks.}
\item {Analyzed simulation data for statistical differences using Pandas and
	visualized data for presentation using Seaborn.}
\item {Presented at the Biannual ACM Research Symposium.}
\end{cvitems}
}

\end{cventries}
